ПАРАЛЛЕЛЬНЫЙ АЛГОРИТМ ДЛЯ ПОЛУЧЕНИЯ РАВНОМЕРНОГО ПРИБЛИЖЕНИЯ РЕШЕНИЙ МНОЖЕСТВА ЗАДАЧ ГЛОБАЛЬНОЙ ОПТИМИЗАЦИИ С НЕЛИНЕЙНЫМИ ОГРАНИЧЕНИЯМИ \footnote{Статья рекомендована к публикации программным комитетом Международной научной конференции <<Параллельные вычислительные технологии (ПаВТ) 2020>>.}

### 2020-02-07 2020/PAVT_Sovrasov/vm_journal/vm_paper.tex
PAVT: update English in the special issue version

\address{$^{1}$South Ural University (pr. Lenina 76, Chelyabinsk, 454080 Russia),\\$^{2}$Lomonosov Moscow State Universisty (GSP-1, Leninskie Gory 1, Moscow, 119991 Russia)}

@@

\begin{abstract}%
  In this work building of a parallel version of a method simultaneously solving a set of
  constrained global optimization problems is considered. The method is built on top of existing
  one by extending it to problems with arbitrary nonlinear constraints and objective
  satisfying the Lipschitz condition.

  \keywordsen{global optimization, parallel computations.}
\end{abstract}

@@

\begin{citationplace}
Sovrasov~V.V., Barkalov~K.A. The \LaTeXe{} Parallel global optimization algorithm for obtaining uniform convergence
when simultaneously solving a set of global optimization problems. Bulletin of the South Ural State University. Series: Computational Mathematics and Software Engineering. 2020. Vol.~X, no.~Y. P.~Z1--Z2. (in Russian) DOI: 10.14529/cmseXXXXXX.
\end{citationplace}

@@

@@

\bibitem{Norkin1992}
{Норкин В. И.}
\newblock О методе Пиявского для решения общей
  задачи глобальной оптимизации //
\newblock Ж. вычисл. матем. и матем. физ. 1992. № 32 С. 992--1006.

>>>>

\address{Lobachevsky State University of Nizhni Novgorod, Russia (pr. Gagarina 23(2), Nizhni Novgorod, 603022 Russia)}

@@

\maketitle{}
\begin{abstract}%
  In this work building of a parallel version of a method simultaneously solving a set of
  constrained global optimization problems is considered. This method converges uniformly
  to solutions of all the problems. That allows the method to arrange computational resources in an
  optimal way, since uniform convergence guarantees approximately equal precision
  of numerical solutions at the whole set of problems at the each iteration of optimization.
  Sets of similar global optimization problems appear for an instance after scalarization
  of multi-objective problems or when a global optimization problem has a discrete parameter
  which takes a finite number of possible values. The considered method uses Peano-type curves
  to transform multidimensional problems into univariate ones. Efficiency of the implemented
  parallel algorithm is evaluated on several sets of synthetically generated constrained global optimization problems.

  \keywordsen{global optimization, parallel computations, derivative-free optimization, uniform convergence}
\end{abstract}

@@

\begin{citationplace}
Sovrasov~V.V., Barkalov~K.A. Parallel global optimization algorithm for obtaining uniform convergence
when simultaneously solving a set of global optimization problems. Bulletin of the South Ural State University. Series: Computational Mathematics and Software Engineering. 2020. Vol.~X, no.~Y. P.~Z1--Z2. (in Russian) DOI: 10.14529/cmseXXXXXX.
\end{citationplace}

@@

\bibitem{Paulavicius2011}
{Paulavivcius R., Zilinskas J., Grothey A.}
\newblock Parallel branch and bound for global optimization with combination of
  lipschitz bounds //
\newblock Optim. Method. Softw. 1997. Vol. 26, No. 3. P. 487--498.
\newblock \doi{10.1080/10556788.2010.551537}

@@

\bibitem{grishaginClass}
{Grishagin V.}
\newblock {Operating characteristics of some global search algorithms}
\newblock // Problems of Stochastic Search. Zinatne, Riga. 1978. (in Russian)

\bibitem{Norkin1992}
{Norkin V. I.}
\newblock Towards Pijavskyj's method for solving common global optimization problem //
\newblock J. Comput. Math. Math. Phys. 1992. Vol. 32, no. 7. P. 992--1006. (in Russian)
